---
title: "Clustering homework"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=FALSE}
library(tidyverse)
library(janitor)
library(ggplot2)
library(broom)
library(factoextra)
```


```{r, include=FALSE}
mail <- read_csv("data/mall_customers.csv") %>% 
  clean_names()
```

```{r, include=FALSE}
glimpse(mail)
```

```{r, include=FALSE}
summary(mail)
```

* You have been provided some customer data from a shopping centre. Do some exploratory analysis on the data. Comment on findings. 

```{r}
mail %>% 
 count(gender) 
```

Female bias but not by much.

```{r}
mail %>% 
  ggplot(aes(x = age)) +
  geom_histogram(col = "white") +
  geom_vline(aes(xintercept = mean(age), 
                 col = "red")) +
  geom_text(x = 40, y = 15, label = "Mean Age",
           color = "black",
           size = 3.5,
           hjust = 0)
```

Mix of ages, mean age is about 36-38.


```{r}
mail %>% 
  ggplot(aes(x = spending_score_1_100, y = annual_income_k)) +
  geom_point()
```

Looks like there could be 5 clusters. 

* We are interested in creating a marketing campaign to target customers based on their spending score and annual income. Perform a k-means clustering to find if there are meaningful clusters in the data to target the customers. 

```{r}
mail_scale <- mail %>% 
  select(annual_income_k, spending_score_1_100) %>% 
  mutate(across(where(is.numeric), scale))

summary(mail_scale)

```


* Perform k-means clustering and chose a value of k.

```{r}
k_max <- 20 

k_clusters <- tibble(k = 1:k_max) %>%
  mutate(
    kclust = map(k, ~ kmeans(mail_scale, .x, nstart = 25)), 
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, augment, mail_scale)
  )

k_clusters
```

```{r}
k_clusters$tidied
```


```{r}
fviz_nbclust(mail_scale, kmeans, method = "wss", nstart = 25)
```
```{r}
fviz_nbclust(mail_scale, kmeans, method = "silhouette", nstart = 25)
```


* Visualise the clustering for your chosen value of k.

```{r}
mail_clusters <- k_clusters %>% 
  unnest(cols = c(augmented)) %>%
  filter(k == 5) 
```


```{r}
mail_clusters %>% 
ggplot(aes(x = annual_income_k, y = spending_score_1_100)) +
  geom_point(aes(col = .cluster))
```


* Do you think the clustering seems a good fit for this data?

> 5 claer clusters, yes this seams a good fit

* Comment on the attributes on one or two of the clusters (maybe even give them a label if you like - like in section 4.1 of the 'Segmentation & clustering intro' lesson). 

> High Rollers: High Income - High Spending
  Savers: High Income - Low Spending
  Middle of the road: Middle Income - Middle Spending
  Living on credit: Low Income -  High Spending
  Make doers: Low Income -  Low Spending



