---
title: "R Notebook"
output: html_notebook
---

```{r include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(janitor)
library(ggplot2)
library(ggpubr)
```

```{r}
regions <- read_csv("raw_data/opendata_inc1519comb_region.csv") %>% 
  clean_names()

area <- read_csv("raw_data/opendata_inc9519_hb.csv") %>% 
  clean_names() %>% 
  mutate(hb = case_when(
    hb == "S92000003" ~ "Scotland",
    hb == "S08000015" ~ "Ayrshire and Arran",
    hb == "S08000016" ~ "Borders",
    hb == "S08000017" ~ "Dumfries and Galloway",
    hb == "S08000019" ~ "Forth Valley",
    hb == "S08000020" ~ "Grampian",
    hb == "S08000022" ~ "Highland",
    hb == "S08000024" ~ "Lothian",
    hb == "S08000025" ~ "Orkney",
    hb == "S08000026" ~ "Shetland",
    hb == "S08000028" ~ "Western Isles",
    hb == "S08000029" ~ "Fife",
    hb == "S08000030" ~ "Tayside",
    hb == "S08000031" ~ "Greater Glasgow and Clyde",
    hb == "S08000032" ~ "Lanarkshire",
    TRUE ~ as.character(NA))) %>%
  filter(!is.na(hb)) %>% 
  mutate(cure_diff_up = crude_rate_upper95pc_confidence_interval - crude_rate,
         cure_diff_down = crude_rate - crude_rate_lower95pc_confidence_interval,
         easr_diff_up = easr_upper95pc_confidence_interval - easr,
         easr_diff_down = easr - easr_lower95pc_confidence_interval,
         wasr_diff_up = wasr_upper95pc_confidence_interval - wasr,
         wasr_diff_down = wasr - wasr_lower95pc_confidence_interval,
         sir_diff_up = sir_upper95pc_confidence_interval - standardised_incidence_ratio,
         sir_diff_down = standardised_incidence_ratio - sir_lower95pc_confidence_interval)
  
scotland <- read_csv("raw_data/opendata_inc9519_scotland.csv") %>% 
  clean_names()

  
comb_hb <- read_csv("raw_data/opendata_inc1519comb_hb.csv") %>% 
  clean_names() %>% 
  mutate(hb = case_when(
    hb == "S92000003" ~ "Scotland",
    hb == "S08000015" ~ "Ayrshire and Arran",
    hb == "S08000016" ~ "Borders",
    hb == "S08000017" ~ "Dumfries and Galloway",
    hb == "S08000019" ~ "Forth Valley",
    hb == "S08000020" ~ "Grampian",
    hb == "S08000022" ~ "Highland",
    hb == "S08000024" ~ "Lothian",
    hb == "S08000025" ~ "Orkney",
    hb == "S08000026" ~ "Shetland",
    hb == "S08000028" ~ "Western Isles",
    hb == "S08000029" ~ "Fife",
    hb == "S08000030" ~ "Tayside",
    hb == "S08000031" ~ "Greater Glasgow and Clyde",
    hb == "S08000032" ~ "Lanarkshire",
    TRUE ~ as.character(NA))) %>%
  filter(!is.na(hb))

geog <- read_csv("raw_data/geography_codes_and_labels_hb2014_01042019.csv") %>% 
  clean_names()
```
standardised_incidence_ratio
<dbl>
sir_lower95pc_confidence_interval
<dbl>
sir_upper95pc_confidence_interval
<dbl>
cure_diff_up

```{r}
glimpse(geog)
```

```{r}
glimpse(regions)
```

```{r}
glimpse(area)
```

```{r}
glimpse(scotland)
```


```{r}
head(area)
unique(area$hb)
```

```{r}
area %>% 
  filter(
         sex %in% "All",
         cancer_site %in% "All cancer types") %>% 
  group_by(hb) %>% 
  ggplot(aes(x = year, y = incidences_all_ages, group = hb, col = hb == "Lanarkshire")) +
  geom_point() +
  geom_line() 
```


```{r}
text <- area %>%
  filter(year == 2005) %>% 
  mutate(label_text = hb)

area %>% 
  filter(
         sex %in% "All",
         cancer_site %in% "All cancer types") %>% 
  group_by(hb) %>% 
  ggplot(aes(x = year, y = incidences_all_ages, group = hb, col = hb == "Borders")) +
  geom_point() +
  geom_line() +
  scale_colour_manual(values = c('grey40', 'red'), guide = "none") +
  geom_text(aes(label = "Borders", x = 2020, y = 500), color = "red") +
  geom_text(aes(label = "Greater \nGlasgow", x = 2020, y = 7000), color = "grey40") +
  geom_text(aes(label = "Dumfries", x = 2020, y = 1000), color = "grey40") +
  geom_text(aes(label = "Lothian", x = 2020, y = 5200), color = "grey40") +
  geom_text(aes(label = "Lanarkshire", x = 2019.5, y = 4500), color = "grey40")
  #geom_label(label = "Borders", x = 2005, y = 500)
  
```
In comparison to other local Health Boards, NHS Borders has a small percentage of the cancer incidences across Scotland

```{r}
incident <- area %>% 
  filter(hb %in% "Borders",
         sex %in% "All",
         cancer_site %in% "All cancer types") %>% 
  ggplot(aes(x = year, y = incidences_all_ages, col = "red")) +
  geom_point() +
  geom_line() +
  #scale_y_continuous(limits = c(570, 930)) +
  geom_smooth(method = "lm", se = FALSE, col = "blue") +
  theme(legend.position="none") 

incident
```


```{r}
crue <- area %>% 
  filter(hb %in% "Borders",
         sex %in% "All",
         cancer_site %in% "All cancer types") %>% 
  ggplot(aes(x = year, y = crude_rate)) +
  geom_point(col = "red") +
  geom_line(col = "red") +
  # scale_y_continuous(limits = c(500, 930),
  #                    breaks = c(600, 700, 800, 900)) +
  
  # geom_line(aes(x = year, y = crude_rate_lower95pc_confidence_interval), col = "dark green") +
  # geom_line(aes(x = year, y = crude_rate_upper95pc_confidence_interval), col = "dark green") +
  
   # geom_ribbon(data=subset(area, year %in% 1995:2019), 
  #         aes(ymin= crude_rate_lower95pc_confidence_interval,
  #             ymax= crude_rate_upper95pc_confidence_interval), fill="blue", alpha=0.5) +
  geom_ribbon(aes(ymin = crude_rate - cure_diff_down, ymax = crude_rate + cure_diff_up), fill = "grey70", alpha=0.5) +
  
  geom_smooth(method = "lm", se = FALSE, col = "blue") +
  theme(legend.position="none")

crue
```

```{r}
crude <- area %>% 
  filter(hb %in% "Borders",
         sex %in% "All",
         cancer_site %in% "All cancer types") %>% 
  ggplot(aes(x = year, y = incidences_all_ages)) +
  geom_point(col = "red") +
  geom_line(col = "red") +
  # scale_y_continuous(limits = c(500, 930),
  #                    breaks = c(600, 700, 800, 900)) +
  #geom_smooth(method = "lm", se = FALSE, col = "blue") +
  geom_point(aes(x = year, y = crude_rate),
             col = "dark green") +
  geom_line(aes(x = year, y = crude_rate),
            col = "dark green") +
  geom_ribbon(aes(ymin = crude_rate - cure_diff_down, 
                  ymax = crude_rate + cure_diff_up), 
              fill = "grey70", alpha=0.5) +
  
  geom_text(aes(label = "Incidences", x = 2019.5, y = 900), color = "red") +
  geom_text(aes(label = "Crude \n Rate", x = 2020, y = 650), color = "dark green") +
  geom_text(aes(label = "Crude \n Rate \n Range", x = 2020, y = 750), color = "grey70")
  
  # guides(colour = guide_legend())
#   geom_smooth(method = "lm", se = FALSE, col = "blue") +
  # theme(legend.key = element_rect(fill = "white", colour = "black"))

crude
```


Focusing in on NHS Borders we can see a steady rise in the number of cancer incidences over the 24 year period. The crude rate that is measured by per 100,000 has lagged behind and not followed this increase since around 2004. 


```{r}
got it working

area %>% 
  filter(hb %in% "Borders",
         sex %in% "All",
         cancer_site %in% "All cancer types") %>% 
  pivot_longer(7:8, names_to = "incedence",
               values_to = "val") %>% 
  ggplot(aes(x = year, y = val, col = incedence)) +
  geom_point() +
  geom_line() 
```


```{r}
easr <- area %>% 
  filter(hb %in% "Borders",
         sex %in% "All",
         cancer_site %in% "All cancer types") %>% 
  ggplot(aes(x = year, y = incidences_all_ages)) +
  geom_point(col = "red") +
  geom_line(col = "red") +
  # scale_y_continuous(limits = c(500, 930),
  #                    breaks = c(600, 700, 800, 900)) +
  #geom_smooth(method = "lm", se = FALSE, col = "blue") +
  geom_point(aes(x = year, y = easr),
             col = "#800080") +
  geom_line(aes(x = year, y = easr),
            col = "#800080") +
  geom_ribbon(aes(ymin = easr - easr_diff_down, 
                  ymax = easr + easr_diff_up), 
              fill = "grey70", alpha=0.5) +
  
  geom_text(aes(label = "Incidences", x = 2019.5, y = 900), color = "red") +
  geom_text(aes(label = "Easr", x = 2020, y = 550), color = "#800080") +
  geom_text(aes(label = "Easr \n Range", x = 2020, y = 600), color = "grey70")

easr
```

```{r}
wasr <- area %>% 
  filter(hb %in% "Borders",
         sex %in% "All",
         cancer_site %in% "All cancer types") %>% 
  ggplot(aes(x = year, y = incidences_all_ages)) +
  geom_point(col = "red") +
  geom_line(col = "red") +
  # scale_y_continuous(limits = c(500, 930),
  #                    breaks = c(600, 700, 800, 900)) +
  #geom_smooth(method = "lm", se = FALSE, col = "blue") +
  geom_point(aes(x = year, y = wasr),
             col = "dark orange") +
  geom_line(aes(x = year, y = wasr),
            col = "dark orange") +
  geom_ribbon(aes(ymin = wasr - wasr_diff_down, 
                  ymax = wasr + wasr_diff_up), 
              fill = "grey70", alpha=0.5) +
  
  geom_text(aes(label = "Incidences", x = 2019.5, y = 900), color = "red") +
  geom_text(aes(label = "Wasr", x = 2020, y = 280), color = "dark orange") +
  geom_text(aes(label = "Wasr \n Range", x = 2020, y = 350), color = "grey70")

wasr
```

```{r}
sir <- area %>% 
  filter(hb %in% "Borders",
         sex %in% "All",
         cancer_site %in% "All cancer types") %>% 
  ggplot(aes(x = year, y = incidences_all_ages)) +
  geom_point(col = "red") +
  geom_line(col = "red") +
  # scale_y_continuous(limits = c(500, 930),
  #                    breaks = c(600, 700, 800, 900)) +
  #geom_smooth(method = "lm", se = FALSE, col = "blue") +
  geom_point(aes(x = year, y = standardised_incidence_ratio),
             col = "dark blue") +
  geom_line(aes(x = year, y = standardised_incidence_ratio),
            col = "dark blue") +
  geom_ribbon(aes(ymin = standardised_incidence_ratio - sir_diff_down, 
                  ymax = standardised_incidence_ratio + sir_diff_up), 
              fill = "grey70", alpha=0.5) +
  
  geom_text(aes(label = "Incidences", x = 2019.5, y = 900), color = "red") +
  geom_text(aes(label = "SIR", x = 2020, y = 100), color = "dark blue") +
  geom_text(aes(label = "SIR \n Range", x = 2019.5, y = 170), color = "grey70")

sir
```


```{r}
crude <- area %>% 
  filter(hb %in% "Borders",
         sex %in% "All",
         cancer_site %in% "All cancer types") %>% 
  ggplot(aes(x = year, y = incidences_all_ages)) +
  geom_point(col = "red") +
  geom_line(col = "red") +
  geom_point(aes(x = year, y = crude_rate),
             col = "dark green") +
  geom_line(aes(x = year, y = crude_rate),
            col = "dark green") +
  geom_ribbon(aes(ymin = crude_rate - cure_diff_down, 
                  ymax = crude_rate + cure_diff_up), 
              fill = "grey70", alpha=0.5) 

crude

easr <- area %>% 
  filter(hb %in% "Borders",
         sex %in% "All",
         cancer_site %in% "All cancer types") %>% 
  ggplot(aes(x = year, y = incidences_all_ages)) +
  geom_point(col = "red") +
  geom_line(col = "red") +
  geom_point(aes(x = year, y = easr),
             col = "dark green") +
  geom_line(aes(x = year, y = easr),
            col = "dark green") +
  geom_ribbon(aes(ymin = easr - easr_diff_down, 
                  ymax = easr + easr_diff_up), 
              fill = "grey70", alpha=0.5) 

easr

wasr <- area %>% 
  filter(hb %in% "Borders",
         sex %in% "All",
         cancer_site %in% "All cancer types") %>% 
  ggplot(aes(x = year, y = incidences_all_ages)) +
  geom_point(col = "red") +
  geom_line(col = "red") +
  geom_point(aes(x = year, y = wasr),
             col = "dark green") +
  geom_line(aes(x = year, y = wasr),
            col = "dark green") +
  geom_ribbon(aes(ymin = wasr - wasr_diff_down, 
                  ymax = wasr + wasr_diff_up), 
              fill = "grey70", alpha=0.5) 

wasr

sir <- area %>% 
  filter(hb %in% "Borders",
         sex %in% "All",
         cancer_site %in% "All cancer types") %>% 
  ggplot(aes(x = year, y = incidences_all_ages)) +
  geom_point(col = "red") +
  geom_line(col = "red") +
  geom_point(aes(x = year, y = standardised_incidence_ratio),
             col = "dark green") +
  geom_line(aes(x = year, y = standardised_incidence_ratio),
            col = "dark green") +
  geom_ribbon(aes(ymin = standardised_incidence_ratio - sir_diff_down, 
                  ymax = standardised_incidence_ratio + sir_diff_up), 
              fill = "grey70", alpha=0.5) 

sir

ggarrange(crude, easr, wasr, sir,
          #labels = c("Crude","European Age-Standardised","World Age-Standardised"," standardised incidence"),
          ncol = 2, nrow = 2)


# I just checked out the patchwork package, and yep you can combine legends really easily.
# The code looks something like
# p1 + p2 + plot_layout(guides = "collect")
```




```{r}
area %>% 
  filter(hb %in% "Borders",
         sex %!in% "All",
         cancer_site %!in% "All cancer types") %>% 
  unique(hb$cancer_site)
```


```{r}
`%!in%` <- negate(`%in%`)

pal <- c("Male" = "#a6bddb", "Female" = "#fa9fb5")

area %>% 
  filter(hb %in% "Borders",
         sex %!in% "All",
         cancer_site %in% "All cancer types") %>% 
  ggplot(aes(x = year, y = incidences_all_ages, fill = sex)) +
  geom_col(position = "dodge", col = "black") +
  scale_fill_manual(values = pal)
```

There's not much difference between the genders, some spikes that can be explained below.

```{r}
biggest_type <- area %>% 
  filter(hb %in% "Borders",
         sex %in% "All",
         cancer_site %!in% "All cancer types") %>%
  group_by(cancer_site) %>% 
  summarise(count = sum(incidences_all_ages)) %>% 
  arrange(desc(count)) %>% 
  # change head to 
  head(7)

area %>% 
  filter(cancer_site %in% c(biggest_type$cancer_site)) %>%
  filter(hb %in% "Borders",
         sex %in% "All",
         cancer_site %!in% "All cancer types") %>% 
  ggplot(aes(x = year, y = incidences_all_ages, col = cancer_site)) +
  geom_point() +
  geom_line() +
  labs(title = "Top 7 Cancers in NHS Borders \n",
       x = "Year",
       y = "Number of incidences \n") +
  theme(plot.title = element_text(hjust = 0.5))
```

There are 51 tpyes of cancer that are recorded across Scotland. Out of all these types of cancer the majority have less than 50 cases a year in NHS Borders

Taking the top 7 types of cancer that are have more than 50 cases a year. They can be split by proactive and reactive approaches

#### Proactive

\* We can see that three of them are based on skin cancers that have like developed from exposed to ultraviolet (UV) radiation from the sun. This can be combated with more publicity encouraging on when and how to using sunscreen, while in the local area or on holiday abroad.

\* Trachea, bronchus and lung cancers, came mainly from direct or passive smoking. This can be combated with more publicity on the dangers of direct or passive smoking to people and their family. Can look at putting more support for people trying to quit. 

#### Reactive

\* 2 are types Bowel cancers, while the cause of these is not known, certain risk factors are strongly linked to the disease, including diet, tobacco smoking and heavy alcohol use.

\* Breast cancer is caused when the DNA in breast cells mutate or change, disabling specific functions that control cell growth and division.

```{r}
biggest_type <- area %>% 
  filter(hb %in% "Borders",
         sex %in% "Male",
         cancer_site %!in% "All cancer types") %>%
  group_by(cancer_site) %>% 
  summarise(count = sum(incidences_all_ages)) %>% 
  arrange(desc(count)) %>% 
  # change head to 
  head(7)

area %>% 
  filter(cancer_site %in% c(biggest_type$cancer_site)) %>%
  filter(hb %in% "Borders",
         sex %in% "Male",
         cancer_site %!in% "All cancer types") %>% 
  ggplot(aes(x = year, y = incidences_all_ages, col = cancer_site)) +
  geom_point() +
  geom_line() +
  labs(title = "Top 7 Cancers in Men, NHS Borders \n",
       x = "Year",
       y = "Number of incidences \n") +
  theme(plot.title = element_text(hjust = 0.5))
```


```{r}
biggest_type <- area %>% 
  filter(hb %in% "Borders",
         sex %in% "Female",
         cancer_site %!in% "All cancer types") %>%
  group_by(cancer_site) %>% 
  summarise(count = sum(incidences_all_ages)) %>% 
  arrange(desc(count)) %>% 
  # change head to 
  head(7)

area %>% 
  filter(cancer_site %in% c(biggest_type$cancer_site)) %>%
  filter(hb %in% "Borders",
         sex %in% "Female",
         cancer_site %!in% "All cancer types") %>% 
  ggplot(aes(x = year, y = incidences_all_ages, col = cancer_site)) +
  geom_point() +
  geom_line() +
  labs(title = "Top 7 Cancers in Women, NHS Borders \n",
       x = "Year",
       y = "Number of incidences \n") +
  theme(plot.title = element_text(hjust = 0.5))
```


```{r}
biggest_type <- area %>% 
  filter(hb %in% "Borders",
         sex %!in% "All",
         cancer_site %!in% "All cancer types") %>%
  group_by(cancer_site) %>% 
  summarise(count = sum(incidences_all_ages)) %>% 
  arrange(desc(count)) %>% 
  # change head to 
  head(8)

area %>% 
  filter(cancer_site %in% c(biggest_type$cancer_site)) %>%
  filter(hb %in% "Borders",
         sex %!in% "All",
         cancer_site %!in% "All cancer types") %>% 
  ggplot(aes(x = year, y = incidences_all_ages, col = sex)) +
  geom_point() +
  geom_line() +
  labs(title = "Top 8 Cancers by Gender \n",
       x = "Year",
       y = "Number of incidences \n") +
  theme(plot.title = element_text(hjust = 0.5)) +
  facet_wrap(~ cancer_site) +
  scale_colour_manual(values = pal)
```

While almost all the cancers are shared equally between the two genders, two cancers breast and prostate have a traditional gender bias on which is effected.  As-well two of the skin cancers have a higher risk in men since around 2005 on wards. This can be a demographic to target to focus the publicity encouraging talked about above or showing the risk 

```{r}
glimpse(comb_hb)
```



```{r}
comb_hb %>% 
  filter(hb %in% "Borders",
         sex %!in% "All",
         cancer_site %in% "All cancer types") %>% 
  pivot_longer(c(7:24),
               names_to = "age_range",
               values_to = "count") %>%
  mutate(age_range = case_when(
    age_range == "incidences_age_under5" ~ "< 5",
    age_range == "incidences_age5to9" ~ "05 to 9",
    age_range == "incidences_age10to14" ~ "10 to 14",
    age_range == "incidences_age15to19" ~ "15 yo 19",
    age_range == "incidences_age20to24" ~ "20 to 24",
    age_range == "incidences_age25to29" ~ "25 to 29",
    age_range == "incidences_age30to34" ~ "30 to 34",
    age_range == "incidences_age35to39" ~ "35 to 39",
    age_range == "incidences_age40to44" ~ "40 to 44",
    age_range == "incidences_age45to49" ~ "45 to 49",
    age_range == "incidences_age50to54" ~ "50 to 54",
    age_range == "incidences_age55to59" ~ "55 to 59",
    age_range == "incidences_age60to64" ~ "60 to 64",
    age_range == "incidences_age65to69" ~ "65 to 69",
    age_range == "incidences_age70to74" ~ "70 to 74",
    age_range == "incidences_age75to79" ~ "75 to 79",
    age_range == "incidences_age80to84" ~ "80 to 84",
    age_range == "incidences_age85and_over" ~ "85 +"
  )) %>% 
  select(hb, cancer_site, sex, year, age_range, count) %>% 
  ggplot(aes(x = age_range, y = count, fill = sex)) +
  geom_col(position = "dodge", col = "black") +
  scale_fill_manual(values = pal) +
  coord_flip() +
  labs(title = "Age Range by Gender \n",
       x = "Number of incidences \n",
       y = "Age Range \n") +
  theme(plot.title = element_text(hjust = 0.5))
  
```

Here we can see the brake down by age and gender showing the older the person is the greater risk they have. While women start by being at higher risk at a younger age older men make up the highest risk of cancer. This adds these ages to the demographic of targets to focus any publicity for proactive and reactive approaches.
 
 
```{r}

biggest_type <- area %>% 
  filter(hb %in% "Borders",
         sex %!in% "All",
         cancer_site %!in% "All cancer types") %>%
  group_by(cancer_site) %>% 
  summarise(count = sum(incidences_all_ages)) %>% 
  arrange(desc(count)) %>% 
  # change head to 
  head(8)


comb_hb %>% 
  filter(cancer_site %in% c(biggest_type$cancer_site)) %>%
  filter(hb %in% "Borders",
         sex %!in% "All",
         cancer_site %!in% "All cancer types") %>% 
  pivot_longer(c(7:24),
               names_to = "age_range",
               values_to = "count") %>%
  mutate(age_range = case_when(
    age_range == "incidences_age_under5" ~ "< 5",
    age_range == "incidences_age5to9" ~ "05 to 9",
    age_range == "incidences_age10to14" ~ "10 to 14",
    age_range == "incidences_age15to19" ~ "15 yo 19",
    age_range == "incidences_age20to24" ~ "20 to 24",
    age_range == "incidences_age25to29" ~ "25 to 29",
    age_range == "incidences_age30to34" ~ "30 to 34",
    age_range == "incidences_age35to39" ~ "35 to 39",
    age_range == "incidences_age40to44" ~ "40 to 44",
    age_range == "incidences_age45to49" ~ "45 to 49",
    age_range == "incidences_age50to54" ~ "50 to 54",
    age_range == "incidences_age55to59" ~ "55 to 59",
    age_range == "incidences_age60to64" ~ "60 to 64",
    age_range == "incidences_age65to69" ~ "65 to 69",
    age_range == "incidences_age70to74" ~ "70 to 74",
    age_range == "incidences_age75to79" ~ "75 to 79",
    age_range == "incidences_age80to84" ~ "80 to 84",
    age_range == "incidences_age85and_over" ~ "85 +"
  ),
  cancer_site = case_when(
    cancer_site == "Basal cell carcinoma of the skin" ~ "Basal cell carcinoma",
    cancer_site == "Squamous cell carcinoma of the skin" ~ "Squamous cell carcinoma",
    TRUE ~ cancer_site)) %>% 
  
  #select(hb, cancer_site, sex, year, age_range, count) %>% 
  ggplot(aes(x = age_range, y = count, fill = sex)) +
  geom_col(position = "dodge", col = "black") +
  scale_fill_manual(values = pal) +
  coord_flip() +
  facet_wrap(~ cancer_site) +
  labs(title = "Age Range by Tpye of Cancer \n",
       x = "Number of incidences \n",
       y = "Age Range \n") +
  theme(plot.title = element_text(hjust = 0.5), 
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())
```
This is a brake down of Cancer type by age reinforces the demographic of targets to focus any publicity for proactive and reactive approaches. 

* Skin and lung cancers both men and women being encouraged to take proactive while young.

* Breast and prostate cancers for women and men respectively should be checked regularly at these ages.
 