---
title: "Text Mining Lab"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---

**Duration: 3 hours**

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center", message = FALSE, warning = FALSE)
```

For this lab you will need the following libraries.

```{r}
library(tidyverse)
library(tidytext)
library(ggwordcloud)
library(hcandersenr)
library(harrypotter)
library(janeaustenr)
```

In this lab we'll be working with Harry Potter data, Jane Austen data, and data from the package `hcandersenr` (this has the text of Hans Christian Andersen fairy tales). We'll also be using a dataset of movie reviews from the `text2vec` package. You'll need to install and then load these packages.

```{r, eval = FALSE}
install.packages("hcandersenr")
install.packages("text2vec")
devtools::install_github("bradleyboehmke/harrypotter")
```

Once you have installed and loaded the package the `hcandersenr` package, you will have access to the data frame `hcandersen_en`. 

```{r}
library(hcandersenr)
hcandersen_en
```

The data from `text2vec` that we want is `movie_review`.

```{r}
library(text2vec)
glimpse(movie_review)
```

# Word clouds in `ggplot`

Create a word cloud of the top words that appear in the book "The Little Mermaid". You will need to

1. Select only "The little mermaid" from the `hcandersen_en` data frame.
2. Unnest the tokens and count the frequency of words
3. Remove stop words
4. Plot this using `ggwordcloud()`, from the package `ggwordcloud`.

```{r}
mermaid <- hcandersen_en %>% 
  filter(book %in% "The little mermaid") %>% 
  unnest_tokens(word, text) %>% 
  anti_join(stop_words) %>%
  count(word) 


  ggwordcloud(mermaid$word, mermaid$n)

```



# Bar chart of top words

Make a bar chart of the top 10 sentiment words in "The Little Mermaid". Make the length of the bars depend on how often the words are said, and make the colour of the bars depend on the sentiment of the word.

```{r}
mermaid %>% 
  inner_join(get_sentiments("afinn")) %>% 
  arrange(desc(n)) %>% 
  head(10) %>% 
  mutate(word = factor(word, 
                       levels = word),
         value = as.factor(value)) %>%
  ggplot(aes(x = word, y = n)) + 
  geom_col(aes(fill = value))
```

```{r}
mermaid %>% 
  inner_join(get_sentiments("bing")) %>% 
  arrange(desc(n)) %>% 
  head(10) %>% 
  mutate(word = factor(word, 
                       levels=word)) %>%
  ggplot(aes(x = word, y = n)) + 
  geom_col(aes(fill = sentiment))
```


## Find combinations

Find the most common bigrams in the Harry Potter book "Chamber of Secrets" that start with "very" followed by a sentiment word from the `"bing"` sentiment list.

```{r}
chamber_of_secrets %>% 
  str() %>% 
  unnest_tokens(word, text)
```
```{r}
phrase <- "very"

chamber_of_secrets %>% 
  unnest_tokens(bigram, phrase, token = "ngrams", n = 2)
```



# Compare Authors - Harder

Use TF-IDF scores to find the 5 words most associated with the three sets of books we've looked at so far (Harry Potter novels, Hans Christian Andersen stories and Jane Austen's novels).

**Hint**: The hard part here is creating a data frame with all the authors. In particular the Harry Potter books require a bit of work to join them all together. Look back at the notes to see how we created a character vector with each book as an element.

# A model with text data - Harder

1. Use `unnest_tokens()` to find all the words in the movie review dataset.
2. Create another data frame with the 50 most common words in this dataset (excluding stop words).
3. Now use `inner_join()`, so that your original data frame contains only the top 50 words.
4. Create dummy variables for each word
5. Now create an appropriate regression model where you predict sentiment using the word dummies. What words are important for predicting sentiment?

**Hint:** What type of model should we use for a binary outcome variable?


# Sentiment arcs - Harder

Create a graph showing smoothed lines that show how the sentiment changes though the following Hans Christian Andersen stories. 

* "The Little Mermaid"
* "Thumbelina"
* "The Snow Queen"
* "The Ugly Duckling"
* "The Princess and the Pea"

[**Hints**:

1. You will need to join with `get_sentiments("afinn")`
2. You may need to create a new column which shows the position of each sentence in the story. 

