---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(ggplot2)
```

```{r}
goodread_books <- read_csv("data/books.csv")
```

```{r}
var(goodread_books)
# Warning in var(books) : NAs introduced by coercion, I'm making them as the colums are CHR not DBL
```

```{r}
names(goodread_books)
```
renamed to make clear and consistent with other columns
```{r}
books <- goodread_books %>% 
  select(1:13) %>% 
  rename(num_of_ratings = ratings_count,
         num_of_reviews = text_reviews_count,
         num_of_pages = num_pages
         )
# renamed to make clear and consistent with other columns
names(books)
```



```{r}
glimpse(books)
```


```{r}
dim(books)
# Over 11k Rows, 13 Column
```

```{r}
head(books)
# Publication data is in US 
```
Checking for NA
```{r}
books %>% 
  summarise(across(everything(), ~ sum(is.na(.))))
# no NA's 
```
Summary
```{r}
summary(books)
```


Top 10 with the average rating
```{r}
high_ratings <- books %>% 
  select(title, average_rating, num_of_ratings, publication_date, authors) %>% 
  arrange(desc(average_rating))  %>% 
  head(10)
  
high_ratings
# The highest ratings are for books that have 5 or less votes that will scu the reading 
```

Top 10 with the median or grater number of votes
```{r}
median_high_ratings <- books %>% 
  select(title, average_rating, num_of_ratings, num_of_reviews, publication_date, authors) %>% 
  filter(num_of_ratings > median(num_of_ratings)) %>% 
  arrange(desc(average_rating))  %>% 
  head(10)
  
median_high_ratings 
# Using the median number as the min
```

Top 10 with the mean or grater number of votes
```{r}
mean_high_ratings <- books %>% 
  select(title, average_rating, num_of_ratings, num_of_reviews, publication_date, authors) %>%  
  filter(num_of_ratings > mean(num_of_ratings)) %>% 
  arrange(desc(average_rating))  %>% 
  head(10)
  
mean_high_ratings 
# Changing to the mean as the min, the top 4 stay the same 
```

Top 10 with the most number of votes
```{r}
most_ratings <- books %>% 
  select(title, average_rating, num_of_ratings, num_of_reviews, publication_date, authors) %>% 
  arrange(desc(num_of_ratings))  %>% 
  head(10)
most_ratings
# These are all new books in them self's 
# seeing the more votes the bigger the spread, more chance for people to love or hate it
```

Top 10 with the most reviews
```{r}
most_reviews <- books %>% 
  select(title, average_rating, num_of_ratings, num_of_reviews, publication_date, authors) %>%
  arrange(desc(num_of_reviews))  %>% 
  head(10)
most_reviews
# This shows the top 10 with the most reviews
```

Number of books published by authors
```{r}
books %>%
  filter(!is.na(rowid)) %>%
  group_by(authors) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
# Number of books published
```


```{r}
books %>%
  filter(!is.na(rowid)) %>%
  group_by(authors) %>%
  summarise(count = n(),
            mean_rating_of_all_books = sum(average_rating)/count) %>%
  arrange(desc(count))
```



P.G. Wodehouse work 
```{r}
books %>% 
  filter(authors == "P.G. Wodehouse" ) %>% 
  group_by(average_rating) %>% 
  arrange(desc(average_rating))
```

```{r}
books %>% 
  filter(authors == "Stephen King" ) %>% 
  group_by(average_rating) %>% 
  arrange(desc(average_rating))
```

Seen S. King had municipal so reran with distinct
```{r}
books %>% 
  filter(authors == "Stephen King" ) %>%
  group_by(average_rating) %>% 
  arrange(desc(average_rating)) %>% 
  distinct(title) 

```


Seen S. King had municipal so reran with distinct
```{r}
books %>%
  
  group_by(authors) %>%
  distinct(title) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
```

# Johny work to change date from chr to dbl
```{r}
books_date_edited <- goodread_books %>% # have change books <- goodread_books
  select(title, ratings_count, text_reviews_count, publication_date) %>%
  mutate(date = as.Date(publication_date, "%m/%d/%Y")) %>%
  arrange(date)

books_date_edited

libarary(lurbridate)

books_date_edited <- goodread_books %>% # have change books <- goodread_books
  select(title, ratings_count, text_reviews_count, publication_date) %>%
  mutate(date = as.Date(publication_date, "%m/%d/%Y"),
         year = year(date)) %>% # Using the package lurbridate reads the just the year and prints that
  arrange(date)

books_date_edited

```

# Louise work is lower rating than long books
```{r}
short_book <- goodread_books %>% # have change books <- goodread_books
  select(title, average_rating, num_pages) %>%
  mutate(length_of_book = case_when(
    num_pages < 200 ~ "under 200",
    num_pages > 200 & num_pages < 400 ~ "200 to 400",
    
    TRUE ~ "above 2000")) %>%
  filter(length_of_book == "200 to 400") %>%
  summarise(low_book_avg_rating = mean(average_rating))


  
long_book <- goodread_books %>% # change main_books_data to goodread_books
  select(title, average_rating, num_pages) %>%
  mutate(length_of_book = case_when(
    num_pages < 600 ~ "under 200",
    num_pages > 600 & num_pages < 800 ~ "600 to 800",
    TRUE ~ "above 2000")) %>%
  filter(length_of_book == "600 to 800") %>%
  summarise(high_book_avg_rating = mean(average_rating))

highest_book_split_rating <- short_book < long_book
highest_book_split_rating

# short book do have a lower rating than long books

# class changes to Louise work to give table 

book_summ <- goodread_books %>% # change main_books_data to goodread_books
  select(title, average_rating, num_pages) %>%
  mutate(length_of_book = case_when(
    num_pages < 200 ~ "0. under 200",
    num_pages >= 200 & num_pages < 400 ~ "1. 200 to 400",
    num_pages >= 400 & num_pages < 600 ~ "2. 400 to 600",
    num_pages >= 600 & num_pages < 800 ~ "3. 600 to 800",
    TRUE ~ "4. above 800")) %>%
  # filter(length_of_book == "200 to 400") %>%
  group_by(length_of_book) %>%
  summarise(avg_rating = mean(average_rating))

book_summ
```

# Ricardo  work
```{r}
efficient_writers <- books %>% 
  group_by(authors, title) %>% 
  summarise(pages_written = sum(num_pages),
            author_av_rating = mean(average_rating),
            efficiency_score = author_av_rating / pages_written) %>%
  mutate(pages_written = if_else(pages_written <100, as.numeric(NA), pages_written)) %>% 
  drop_na(.) %>% 
  slice_max(efficiency_score)
```


# Not working trying to use distinct but kill the code when added
```{r}
books %>%
  filter(!is.na(rowid)) %>%
  group_by(authors) %>%
  distinct(title) %>%
  summarise(count = n(),
            mean_rating_of_all_books = sum(average_rating)/count) %>%
  arrange(desc(count))
```


# Not working authors_by_book
```{r}
# authors_by_book <- group_by(books, authors)
# authors_by_book
# 
# #summarise(authors_by_book, character_count = n())
# summarise(authors_by_book, unique() = n())

```


# Not working by_book for authors, works by taking the last %>% out
```{r}
by_book <- books %>%
  select(authors) %>%
  summary(unique(authors))

by_book
```

# Not working hfsd for authors
```{r}
# hfsd <- books %>% 
#   select(authors) %>% 
#   summary(unique(authors)) %>%
# hfsd
```

```{r}

```


# Not working pub_year for year
```{r}
# pub_year <- books %>% 
#   select(1:13) %>% 
#   #rename(publication_year = publication_date) %>% 
#   mutate_at(publication_date, as.Date, format = "%d-%m-%Y")
#         
#   #format(as.Date(nzd$date, format = "%d/%m/%Y")
#           
# pub_year
```

# Extra library don't help
```{r}
# library(stringi)
# library(stringr)
```

# down the rabbit hole still can't get the year
```{r}
#as.numeric(as.character(publication_date)

#mutate(books, publication_year = as.numeric(publication_date))
#mutate(books, publication_year = str_sub(publication_date, -4, -1) 
# x <-  3/14/2006
# str_sub(x, start = -4)
# #str_sub(x, -4, -1)
```

