---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(ggplot2)
```

```{r}
goodread_books <- read_csv("data/books.csv")
```

```{r}
var(goodread_books)
# Warning in var(books) : NAs introduced by coercion, I'm making them as the colums are CHR not DBL
```

```{r}
names(goodread_books)
```

```{r}
books <- goodread_books %>% 
  select(1:13) %>% 
  rename(num_of_ratings = ratings_count,
         num_of_reviews = text_reviews_count,
         num_of_pages = num_pages
         )
# renamed to make clear and consistent with other columns
names(books)
```



```{r}
glimpse(books)
```


```{r}
dim(books)
# Over 11k Rows, 13 Column
```

```{r}
head(books)
# Publication data is in US 
```
Checking for NA
```{r}
books %>% 
  summarise(across(everything(), ~ sum(is.na(.))))
# no NA's 
```
Summary
```{r}
summary(books)
```


Top 10 with the average rating
```{r}
high_ratings <- books %>% 
  select(title, average_rating, num_of_ratings, publication_date, authors) %>% 
  arrange(desc(average_rating))  %>% 
  head(10)
  
high_ratings
# The highest ratings are for books that have 5 or less votes that will scu the reading 
```

Top 10 with the median or grater number of votes
```{r}
median_high_ratings <- books %>% 
  select(title, average_rating, num_of_ratings, num_of_reviews, publication_date, authors) %>% 
  filter(num_of_ratings > median(num_of_ratings)) %>% 
  arrange(desc(average_rating))  %>% 
  head(10)
  
median_high_ratings 
# Using the median number as the min
```

Top 10 with the mean or grater number of votes
```{r}
mean_high_ratings <- books %>% 
  select(title, average_rating, num_of_ratings, num_of_reviews, publication_date, authors) %>%  
  filter(num_of_ratings > mean(num_of_ratings)) %>% 
  arrange(desc(average_rating))  %>% 
  head(10)
  
mean_high_ratings 
# Changing to the mean as the min, the top 4 stay the same 
```

Top 10 with the most number of votes
```{r}
most_ratings <- books %>% 
  select(title, average_rating, num_of_ratings, num_of_reviews, publication_date, authors) %>% 
  arrange(desc(num_of_ratings))  %>% 
  head(10)
most_ratings
# These are all new books in them self's 
# seeing the more votes the bigger the spread, more chance for people to love or hate it
```

Top 10 with the most reviews
```{r}
most_reviews <- books %>% 
  select(title, average_rating, num_of_ratings, num_of_reviews, publication_date, authors) %>%
  arrange(desc(num_of_reviews))  %>% 
  head(10)
most_reviews
# This shows the top 10 with the most reviews
```

Number of books published by authors
```{r}
books %>%
  filter(!is.na(rowid)) %>%
  group_by(authors) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
# Number of books published
```


```{r}
books %>%
  filter(!is.na(rowid)) %>%
  group_by(authors) %>%
  summarise(count = n(),
            mean_rating_of_all_books = sum(average_rating)/count) %>%
  arrange(desc(count))
```



P.G. Wodehouse work 
```{r}
books %>% 
  filter(authors == "P.G. Wodehouse" ) %>% 
  group_by(average_rating) %>% 
  arrange(desc(average_rating))
```

```{r}
books %>% 
  filter(authors == "Stephen King" ) %>% 
  group_by(average_rating) %>% 
  arrange(desc(average_rating))
```

Seen S. King had municipal so reran with distinct
```{r}
books %>% 
  filter(authors == "Stephen King" ) %>%
  group_by(average_rating) %>% 
  arrange(desc(average_rating)) %>% 
  distinct(title) 

```


Seen S. King had municipal so reran with distinct
```{r}
books %>%
  
  group_by(authors) %>%
  distinct(title) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
```


# Not working trying to use distinct but kill the code when added
```{r}
books %>%
  filter(!is.na(rowid)) %>%
  group_by(authors) %>%
  distinct(title) %>%
  summarise(count = n(),
            mean_rating_of_all_books = sum(average_rating)/count) %>%
  arrange(desc(count))
```


# Not working authors_by_book
```{r}
# authors_by_book <- group_by(books, authors)
# authors_by_book
# 
# #summarise(authors_by_book, character_count = n())
# summarise(authors_by_book, unique() = n())

```


# Not working by_book for authors
```{r}
# by_book <- books %>% 
#   select(authors) %>% 
#   summary(unique(authors)) %>%
#   
# by_book
```

# Not working hfsd for authors
```{r}
# hfsd <- books %>% 
#   select(authors) %>% 
#   summary(unique(authors)) %>%
# hfsd
```

# Not working pub_year for year
```{r}
# pub_year <- books %>% 
#   select(1:13) %>% 
#   #rename(publication_year = publication_date) %>% 
#   mutate_at(publication_date, as.Date, format = "%d-%m-%Y")
#         
#   #format(as.Date(nzd$date, format = "%d/%m/%Y")
#           
# pub_year
```

# Extra library don't help
```{r}
# library(stringi)
# library(stringr)
```

# down the rabbit hole still can't get the year
```{r}
#as.numeric(as.character(publication_date)

#mutate(books, publication_year = as.numeric(publication_date))
#mutate(books, publication_year = str_sub(publication_date, -4, -1) 
# x <-  3/14/2006
# str_sub(x, start = -4)
# #str_sub(x, -4, -1)
```

