---
title: "Text Mining Homework"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    code_folding: hide
  pdf_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = "center", message = FALSE, warning = FALSE)
```



```{r, include=FALSE}
library(tidyverse)
library(tidytext)
library(janeaustenr)
library(janitor)
library(ggplot2)
```

```{r}
austen_books <- austen_books()
```

```{r}
glimpse(austen_books)
```

```{r}
unique(austen_books$book)
```

# MVP

Using the dataset `austen_books()` from the package `janeaustenr`:

1. Find the most common words in both Pride & Prejudice and Sense & Sensibility.

<br>
```{r}
austen_books %>% 
  filter(book %in% c("Sense & Sensibility", "Pride & Prejudice")) %>% 
  unnest_tokens(word, text) %>%
  count(word, sort = TRUE)
```

<br>

2. Find the most common words in both Pride & Prejudice and Sense & Sensibility, not including stop words.

<br>
```{r}
austen_books %>% 
  filter(book %in% c("Sense & Sensibility", "Pride & Prejudice")) %>% 
  unnest_tokens(word, text) %>%
  count(word, sort = TRUE) %>%
  anti_join(stop_words)
```
<br>

3. Find the most common sentiment words in both Pride & Prejudice and Sense & Sensibility.

<br>
```{r}
afinn <- austen_books %>% 
  filter(book %in% c("Sense & Sensibility", "Pride & Prejudice")) %>% 
  unnest_tokens(word, text) %>%
  count(word, sort = TRUE) %>%
  anti_join(stop_words) %>% 
  inner_join(get_sentiments("afinn")) %>% 
  head(10) %>%
  mutate(word = factor(word, 
                       levels = word),
         value = as.factor(value))

afinn

afinn %>% 
  ggplot(aes(y = word, x = n)) + 
  geom_col(aes(fill = value)) +
  labs(x = "Count",
       y = "Common Words",
       title = "Common Words by Sentiment") +
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
bing <- austen_books %>% 
  filter(book %in% c("Sense & Sensibility", "Pride & Prejudice")) %>% 
  unnest_tokens(word, text) %>%
  count(word, sort = TRUE) %>%
  anti_join(stop_words) %>% 
  inner_join(get_sentiments("bing")) %>% 
  head(10) %>%
  mutate(word = factor(word, 
                       levels = word))

bing

bing %>% 
ggplot(aes(y = word, x = n)) + 
  geom_col(aes(fill = sentiment)) +
  labs(x = "Count",
       y = "Common Words",
       title = "Common Words by Sentiment") +
  theme(plot.title = element_text(hjust = 0.5))
```
<br>

# Extension

Taking your results above. Can you create a plot which visualises the differences between the books?  

<br>
```{r}
austen_books %>% 
  unnest_tokens(word, text) %>%
  filter(book %in% c("Sense & Sensibility", "Pride & Prejudice"),
         word %in% c(afinn$word, bing$word)) %>% 
  group_by(book) %>% 
  count(word, sort = TRUE) %>%
  mutate(word = factor(word, 
                       levels = word)) %>% 
  ggplot(aes(y = word, x = n)) + 
  geom_col(aes(fill = book), position = "dodge") +
  labs(x = "Count",
       y = "Common Words",
       title = "Common Words by Book") +
  theme(plot.title = element_text(hjust = 0.5))

```

```{r}
austen_books %>% 
  unnest_tokens(word, text) %>%
  filter(book %in% c("Sense & Sensibility", "Pride & Prejudice"),
         word %in% c(afinn$word)) %>% 
  group_by(book) %>% 
  count(word, sort = TRUE) %>%
  mutate(word = factor(word, 
                       levels = word)) %>% 
  ggplot(aes(y = word, x = n)) + 
  geom_col(aes(fill = book), position = "dodge") +
  labs(x = "Count",
       y = "Common Words",
       title = "Common Words by Book & Afinn Sentiment") +
  theme(plot.title = element_text(hjust = 0.5))
```


```{r}
austen_books %>% 
  unnest_tokens(word, text) %>%
  filter(book %in% c("Sense & Sensibility", "Pride & Prejudice"),
         word %in% c(bing$word)) %>% 
  group_by(book) %>% 
  count(word, sort = TRUE) %>%
  mutate(word = factor(word, 
                       levels = word)) %>% 
  ggplot(aes(y = word, x = n)) + 
  geom_col(aes(fill = book), position = "dodge") +
  labs(x = "Count",
       y = "Common Words",
       title = "Common Words by Book & Bing Sentiment") +
  theme(plot.title = element_text(hjust = 0.5))
```




