---
title: "The Titanic"
output: html_notebook
---

```{r}
library(prob)
library(gtools)
library(tidyverse)
library(janitor)
```

```{r}
titanic <- read_csv("data/titanic.csv")
```

#1.1 The Titanic
Some time after the disaster a journalist wrote that crew members were more likely to have survived the sinking than passengers. This was disputed by a descendant of one of the surviving crew members, who suggested that the opposite was true, i.e. passengers were more likely to have survived than crew.

#Question
Calculate the conditional probabilities prob(survived∣crew) and prob(survived∣passenger)

to settle this dispute.

Have a look at the distinct values of the class variable, this will tell you whether each individual was a passenger (1st, 2nd or 3rd class) or a member of the crew (treat restaurant staff as crew)


```{r}
head(titanic)
```


```{r}
titanic %>% 
  count(class)
```

```{r}
titanic %>% 
  filter(survived %in% "yes") %>% 
  count(class)
```

```{r}
class_list <- titanic %>% 
  mutate(crew = if_else(str_detect(class, 
                                   "[0-9][a-z]{2}"), 
                                   "passengers", "crew"))
class_list
```

```{r}
class_list %>% 
  group_by(survived) %>% 
  count(crew)
```
```{r}
# 500 passengers survived out of 1317. Giving 38% change of survival
500/1317 
```

```{r}
# 211 crew survived out of 890. Giving 24% change of survival
211/890
```


```{r}
crew_pass <- class_list %>% 
  tabyl(survived, crew) 

crew_pass
```

```{r}
crew_pass <- crew_pass %>% 
  adorn_totals(where = c("row", "col"))

crew_pass
```

```{r}
crew_pass <- crew_pass %>% 
adorn_percentages(denominator = "all")

crew_pass

# Out of the people on broad 32% survived 23% of them passangers and 10% crew.
# Out of the people on broad 68% died 37% of them passangers and 31% crew.
```



```{r}
prob_pass <- class_list %>% 
  filter(crew %in% "passengers") %>% 
  summarise(prob = sum(survived == "yes") / n())

prob_pass

# As above 38% change of survival, 500 passengers survived out of 1317.  
```

```{r}
prob_crew <- class_list %>% 
  filter(crew %in% "crew") %>% 
  summarise(prob = sum(survived == "yes") / n())

prob_crew
# As above 24% change of survival, 211 crew survived out of 890.
```

```{r}
prob_class <- class_list %>% 
  group_by(class) %>% 
  summarise(prob = sum(survived == "yes") / n()) %>% 
  arrange(desc(prob))

prob_class
```

```{r}
prob_staff <- class_list %>% 
  group_by(crew) %>% 
  summarise(prob = sum(survived == "yes") / n()) %>% 
  arrange(desc(prob))

prob_staff
```


```{r}
prob_gender <- class_list %>% 
  group_by(gender) %>% 
  summarise(prob = sum(survived == "yes") / n()) %>% 
  arrange(desc(prob))

prob_gender
```

```{r}
age_grouped <- class_list %>% 
  #mutate(age_group = when(age == NA_integer_, "unknown")) %>% 
  mutate(age_group = if_else(age < 10, "under_10",
                             if_else(age < 20, "under_20",
                             if_else(age < 30, "20's",
                             if_else(age < 40, "30's",
                             if_else(age < 50, "40's",
                             if_else(age < 60, "50's",
                             if_else(age < 70, "60's",
                             if_else(age < 80, "70's",
                             if_else(age < 90, "80's",
                             if_else(age < 100, "90's", "over 100"
                             ))))))))))) 
  
         
         
age_grouped
```

```{r}
age_grouped %>% 
  group_by(age_group) %>% 
  summarise(prob = sum(survived == "yes") / n()) %>% 
  arrange(desc(prob))
```

```{r}
age_grouped %>% 
  filter(is.na(age_group))
```

# Answer
No. More passangers survived than crew, 38% of the passangers to 24% of the crew. 

Out of the people on broad 32% survived, 23% of them passangers and 10% crew.

Both ways passengers were more likely to have survived than crew. While the deck crew did have a higher probabilitie of survival out of the classes at 65%,probably this is due to the fact they will have had to man the lifeboats. So the journalist might have just looked at this stat.

Female's were about 3.6 times more likly to survive at 73% to male's 20%.

Under 10's where the highest age group to survive.


