---
title: "Homework - CIs"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = 'center')
```

```{r}
library(tidyverse)
library(janitor)
library(infer)
library(ggplot2)
```



<hr>

# MVP

Now we'll go back to CI creation in the normal fashion. We'll take the `ames` data from the CIs lab earlier today and regard it now as a **sample**, we won't be drawing any smaller samples from within it. This is the usual situation in an analysis: you use all the data available to you!

<br>

**Task 1.**  
Load the data again, `clean_names()`, and re-familiarise yourself with it
```{r}
ames <- read_csv("data/ames.csv") %>% 
  clean_names()
```

<br>

**Task 2.**  
Investigate the distribution of `lot_area`. Is the distribution roughly normal? If not, what problems do you find?
```{r}
ames %>% 
  ggplot(aes(x = lot_area)) +
  geom_histogram(col = "black", fill = "red", alpha = 0.7)
```


<br>

**Task 3.**  
Compute and visualise a bootstrap sampling distribution for the `mean(lot_area)` of the sold houses.
```{r}
ames_infer <- ames %>% 
  specify(response = lot_area) %>% 
  generate(reps = 5000, type = "bootstrap") %>% 
  calculate(stat = "mean")

ames_infer %>% 
  summarise(mean(stat))
```

<br>

**Task 4.**  
Use your bootstrap distribution to calculate a $95\%$ CI for `mean(lot_area)`, and visualise it on the distribution
```{r}
ames_infer_95 <- ames_infer %>% 
  get_ci(level = 0.95, type = "percentile")

ames_infer_95
```

<br>

**Task 5.**  
You would like to know the `mean(lot_area)` of the sold houses with higher confidence. Calculate the $99\%$ CI for this variable (you can re-use your bootstrap distribution from above). Is it narrower or broader than the $95\%$ CI? Does that make sense?
```{r}
ames_infer_99 <- ames_infer %>% 
  get_ci(level = 0.99, type = "percentile")

ames_infer_99

# broader as the outlining data pulling it out
```

<br>

**Task 6.**  
Calculate the point estimate of the `mean(lot_area)`
```{r}
mean_ames <- ames_infer %>% 
  summarise(mean = mean(stat))
mean_ames
```

<hr>

# Extension

<br>
```{r}
names(ames)
```

**Task 1.**  
Calculate a point estimate and $95\%$ CI for the proportion of houses in the data built before 1920.  Does the number of `reps` you use matter? [Investigate `reps` from $200$ up to $50000$, memory of your laptop permitting].
<br><br>
```{r}
yr_1920 <- ames %>%
  filter(year_built < 1920)


# 
# yr_infer <- yr_1920 %>% 
#   specify(response = reps) %>% 
#   
```

```{r}
ames %>% 
  ggplot(aes(x = year_built)) + 
  geom_histogram(col = "black", fill = "red", alpha = 0.7) 
```


```{r}
yr_built <- ames %>% 
  summarise(prop_1920 = sum(year_built < 1920)/ n())

yr_built
```

```{r}
yr_infer_200 <- yr_1920 %>% 
  specify(response = year_built) %>% 
  generate(reps = 200, type = "bootstrap") %>% 
  calculate(stat = "mean")

yr_infer_5000 <- yr_1920 %>% 
  specify(response = year_built) %>% 
  generate(reps = 5000, type = "bootstrap") %>% 
  calculate(stat = "mean")

yr_infer_200
yr_infer_5000
```

```{r}
yr_200_ci <- yr_infer_200 %>% 
  get_ci(level = 0.95, type = "percentile")

yr_5000_ci <- yr_infer_5000 %>% 
  get_ci(level = 0.95, type = "percentile")

yr_200_ci
yr_5000_ci
```

```{r}
yr_infer_200 %>% 
  visualise(bins = 30) +
  shade_confidence_interval(endpoints = yr_200_ci) +
  labs(x = "Year Built",
       y = "Number Built")

yr_infer_5000 %>% 
  visualise(bins = 30) +
  shade_confidence_interval(endpoints = yr_5000_ci) +
  labs(x = "Year Built",
       y = "Number Built")
```


```{r}
mean_yr_200 <- yr_infer_200 %>% 
  summarise(mean = mean(stat))

mean_yr_5000 <- yr_infer_5000 %>% 
  summarise(mean = mean(stat))


mean_yr_200
mean_yr_5000
```

